\newpage
\addcontentsline{toc}{section}{Tài liệu tham khảo} \bibliographystyle{plain}
\begin{thebibliography}{9}

\bibitem{1}
\href{https://www.forestadmin.com/blog/user-authentication-a-guide-for-developers/}{Lanchec, S. (2024, June 5). User Authentication: a guide for developers. Forest Admin Blog. https://www.forestadmin.com/blog/user-authentication-a-guide-for-developers/}

\bibitem{2}
\href{https://workos.com/blog/the-five-different-types-of-authentication}{The five different types of authentication — WorkOS. (n.d.). WorkOS. https://workos.com/blog/the-five-different-types-of-authentication}

\bibitem{3}
\href{https://auth0.com/intro-to-iam/what-is-authentication}{What is Authentication? Definition and uses - Auth0. (n.d.). Auth0. https://auth0.com/intro-to-iam/what-is-authentication}

\bibitem{4}
\href{https://www.geeksforgeeks.org/what-is-user-authentication-and-why-is-it-important/}{GeeksforGeeks. (2024, June 6). What is User Authentication, and Why is it Important? GeeksforGeeks. https://www.geeksforgeeks.org/what-is-user-authentication-and-why-is-it-important/}

\bibitem{5}
\href{https://frontegg.com/blog/authentication\#API_Authentication_Methods}{Frontegg. (2025, January 9). Authentication: What It is and How It Works | Frontegg. Frontegg. \url{https://frontegg.com/blog/authentication\#API_Authentication_Methods}}

\bibitem{6}
\href{https://goteleport.com/blog/authentication-best-practices/}{Sakshyam Shah. (2022, February 25). 6 Authentication best practices. Teleport. https://goteleport.com/blog/authentication-best-practices/}

\bibitem{7}
\href{https://software.intel.com/sites/manageability/AMT_Implementation_and_Reference_Guide/default.htm?turl=WordDocuments%2Fintroductiontokerberosauthentication.htm}{Intel® AMT SDK implementation and Reference Guide. (n.d.). https://software.intel.com/sites/manageability/AMT\_Implementation\_and\_Reference\_Guide\\/default.htm?turl=WordDocuments\%2Fintroductiontokerberosauthentication.htm}

\bibitem{8}
\href{https://www.vaadata.com/blog/what-is-kerberos-kerberos-authentication-explained/}{Author, V., \& Author, V. (2024, October 8). What is Kerberos? Kerberos Authentication Explained. VAADATA - Ethical Hacking Services. \url{https://www.vaadata.com/blog/what-is-kerberos-kerberos-authentication-explained/}}

\bibitem{9}
\href{https://en.wikipedia.org/wiki/Kerberos_(protocol)}{Wikipedia contributors. (2025, February 8). Kerberos (protocol). Wikipedia. https://en.wikipedia.org/wiki/Kerberos\_(protocol)}
\end{thebibliography}